Rotating Stars from \Kepler Observed with Gaia

### 2016-09-21 paper/ms.tex
add paper

%%%%%%%%%%%%%%%%%%%%%%
\title{Demonstrating the Stellar Rotation \Kepler--Gaia }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Rotating stars. 
overlap between samples
two 
\end{abstract}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{data}

@@

using CDS X-Match service
tgas = J/ApJS/211/24/table1 \& I/337/tgas
gaia = J/ApJS/211/24/table1 \& I/337/gaia

%%%%%%%%%%%%
\section{Determining Flare Energies}

@@

%%%%%%%%%%%%
\section{Determining Flare Energies}

\begin{figure}[]
\centering
\includegraphics[width=5.3in]{fig2.png}
\caption{
isochrones from \citet{bressan2012}
}
\label{fig:all}
\end{figure}

%%%%%%%%%%%%
\section{Determining Flare Energies}

\begin{figure}[]
\centering
\includegraphics[width=4in]{fig3.png}
\caption{
}
\label{fig:all}
\end{figure}

%%%%%%%%%%%%
\section{Determining Flare Energies}

\begin{figure}[]
\centering
\includegraphics[width=5.3in]{fig4.png}
\caption{
}
\label{fig:all}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%
\title{Rotating Stars from \Kepler Observed with Gaia}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Rotating stars. 
overlap between samples

\end{abstract}

@@

of course, Kepler useful for calibrations for Gaia, e.g. log(g) \citep{creevey2013}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{The \Kepler--Gaia Data}

using CDS X-Match service, we match the catalogs from 
%tgas = J/ApJS/211/24/table1 \& I/337/tgas
%gaia = J/ApJS/211/24/table1 \& I/337/gaia

@@

%%%%%%%%%%%%
\section{Selecting Main Sequence Stars}

first we create the HR diagram, using the absolute Gaia magnitudes from the TGAS parallaxes, and the temperatures reported from McQ14

\begin{figure}[]
\centering
\includegraphics[width=5.3in]{fig2.png}
\caption{
isochrones from \citet{bressan2012}
}
\label{fig:HR}
\end{figure}

\begin{figure}[]
\centering
\includegraphics[width=4in]{fig3.png}
\caption{
}
\label{fig:hist}
\end{figure}

%%%%%%%%%%%%
\section{Extending the Spin-Down Gap}

this feature first observed in rotation period by \citet{mcquillan2013} for M dwarfs

here we show it appears to extended to nearby higher mass stars in the \Kepler field.

the reason this feature did not appear in earlier \Kepler studies is the inability to select main sequence stars from turn-off or subgiants using the KIC

\begin{figure}[]
\centering
\includegraphics[width=5.3in]{fig4.png}
\caption{
}
\label{fig:gyro}
\end{figure}
